Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-01 ms.tex
compare spectra
transmission spectrum

\subsection{Transmission Spectrum}
The transmission spectrum is challenging to measure due to contaminating flux from the planet's nightside. We will report WASP-103b's transmission spectrum in a companion paper. The 
FIXME

@@

\begin{figure*}
	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.  The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth). Row (2) indicates the ratio of pressures probed in and out of the water band. On the dayside, the opacity out of the water band is filled in by absorption from H- and TiO/VO. Rows (3-4) show the abundances of H$_2$O and H-. At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.}
\label{fig:GCMabundance}
\end{figure*}

@@

We also used three brown dwarfs/low mass stars for comparison. We chose the field sources: 2MASS J13204427+0409045, (1320+0409) an optical L3, 2MASS J04285096-2253227 (0428-2253) an optical L0.5 and 2MASS J00034227-2822410 (0003-2822) an optical M8 \citep[see][]{filippazzo15}.  We then used all currently available photometric, astrometric, and spectroscopic data for each source to evaluate fundamental parameters such as mass, $T_\mathrm{eff}$ and log $g$ \citep{filippazzo15, faherty16} and create flux-calibrated spectral energy distributions.  For 1320+0409 we used SDSS, WISE and 2MASS photometry along with the optical spectrum from \cite{reid08}, the near infrared spectrum from \cite{bardalez14}, and the parallax reported in \cite{2012ApJ...752...56F}. For 0428-2253 we used 2MASS, DENIS and WISE photometry along with the optical spectrum from \cite{2003A&A...403..929K} the near infrared spectrum from \cite{bardalez14} and the parallax reported in \cite{2014AJ...147...94D}, and for 0003-2822 we used 2MASS and WISE photometry along with the optical spectrum from \cite{2007AJ...133..439C} the near infrared spectrum from \cite{2018AJ...155...34C}, and the parallax reported in \cite{2010AJ...139..176F}.  Coincidentally, both 1320+0409 and 0003-2822 are widely separated ($> 2000$ AU) companions to K2 and G8 stars respectively.  All data was gathered from the Brown Dwarfs in New York City (BDNYC) database \citep{filippazzo16}\footnote{The BDNYC Database: \url{http://database.bdnyc.org/}}.  At the assumed field ages of each source, 0003-2822 would be above the nuclear burning boundary (star) while 1320+0409 would be below (brown dwarf).  0428-2253 is likely a star but at a slightly younger field age could be a brown dwarf.

>>>>

\subsection{Transmission Spectrum}
Each phase curve observation includes a transit of WASP-103b. The transmission spectrum is challenging to measure robustly due to contaminating flux from the planet's nightside. 
\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{Transmission spectrum of WASP-103b.}
\label{fig:tspec}
\end{figure}

@@

\begin{figure*}
	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.pdf}
	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.  The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth). FIXME: Row (2) indicates the ratio of pressures probed in and out of the water band. On the dayside, the opacity out of the water band is filled in by absorption from H- and TiO/VO. Rows (3-4) show the abundances of H$_2$O and H-. At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.}
\label{fig:GCMabundance}
\end{figure*}

@@

We also used three brown dwarfs/low mass stars for comparison. We chose the field sources: 2MASS J13204427+0409045, (1320+0409) an optical L3, 2MASS J04285096-2253227 (0428-2253) an optical L0.5 and 2MASS J00034227-2822410 (0003-2822) an optical M8 \citep[see][]{filippazzo15}.  We then used all currently available photometric, astrometric, and spectroscopic data for each source to evaluate fundamental parameters such as mass, $T_\mathrm{eff}$ and log $g$ \citep{filippazzo15, faherty16} and create flux-calibrated spectral energy distributions.  For 1320+0409 we used SDSS, WISE and 2MASS photometry along with the optical spectrum from \cite{reid08}, the near infrared spectrum from \cite{bardalez14}, and the parallax reported in \cite{2012ApJ...752...56F}. For 0428-2253 we used 2MASS, DENIS and WISE photometry along with the optical spectrum from \cite{2003A&A...403..929K} the near infrared spectrum from \cite{bardalez14} and the parallax reported in \cite{2014AJ....147...94D}, and for 0003-2822 we used 2MASS and WISE photometry along with the optical spectrum from \cite{2007AJ....133..439C} the near infrared spectrum from \cite{2018AJ....155...34C}, and the parallax reported in \cite{2010AJ....139..176F}.  Coincidentally, both 1320+0409 and 0003-2822 are widely separated ($> 2000$ AU) companions to K2 and G8 stars respectively.  All data was gathered from the Brown Dwarfs in New York City (BDNYC) database \citep{filippazzo15}\footnote{The BDNYC Database: \url{http://database.bdnyc.org/}}.  At the assumed field ages of each source, 0003-2822 would be above the nuclear burning boundary (star) while 1320+0409 would be below (brown dwarf).  0428-2253 is likely a star but at a slightly younger field age could be a brown dwarf.
